Understanding Probabilistic Topic Models by Simulation

### 2018-01-09 paper/doc/doc2.tex
step

Social networks such as Facebook are becoming more and more important for online news services: an increasing number of their readers access the news pages via links in the networks. Users of Facebook, for example, can use their profile to share links to external websites - such as news portals - with their online friends. This has led to the development of social media becoming an important generator of traffic for content providers. In Germany, 94\% of online shared news articles in 2015 are distributed via Facebook, followed by Twitter with 3.5\% and Google+ with 2.3\% \citep{schiller_development_2016}.

The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues. For this reason, news agencies are particularly interested in finding out which topics are more likely shared on these platforms. \citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic. FOCUS Online for example is targeted for articles from politics and business, while sports news is more likely to be shared from Bild.de.

While these pre-defined resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics. Especially if the articles originate from different news portals. Furthermore, articles can contain more than one topic. We use a structural topic model to reveal the underlying topics of a collection of articles, and how the articles exhibit them. We then estimate the effect of topic prevalence on the number of Facebook shares. We use a data set of online news articles about domestic politics dated from 01.06.2017 to 22.11.2017\footnote{German federal elections took place on 24th of September 2017.} from seven German content providers: Bild.de, Die Welt, Focus Online, Spiegel Online, Stern.de, Zeit Online and Tagesschau.de. They are all providers of online news, whereby Tagesschau.de is the only publicly funded service. The latter was also included in the study to verify whether the topics differ when the content is created on the basis of a different business model.

Mapping raw text to one or more topics, without having prior knowledge on what those topics are, translates to an unsupervised classification problem on natural language. Topic models generate low-dimensional representations of data and can uncover interesting latent structure in large text datasets. They are popular tools for automatically identifying prominent themes in text. Within topic models the Latent Dirichlet Allocation (LDA) is a widely used technique, where each document (article) is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms, represented by the topic-term distribution \citep{blei_latent_2003}. \citet{roberts_model_2016} extents the base idea of LDA by developing a structural topic model (STM) that allows to incorporate external variables that effect both topical content and topical prevalence. We use this approach to analyze online news about the german federal elections, where we allow prevalence of topics to vary across newswire services. We then estimate the effect of topical prevalence (the posterior document-topic distribution) on the number of Facebook shares.

Figure \ref{fig_research_strat} gives an overview of the applied research strategy. Chapter \ref{ch_model} explains the generative process of the mixed membership model and the results of this process are presented in chapter \ref{ch_results}. Chapter \ref{ch_data} contains a description of the text data and how it was pre-processed in order to use it as input variable.  Chapter \ref{ch_regression} describes how we regress the estimated probabilities of topic prevalence of a document on the times, this document was shared on Facebook.

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.95\textwidth]{../figs/research_strategy.pdf} 
	\caption{Research Strategy}
	\label{fig_research_strat}
\end{figure}

@@

Advertising-supported media such as online newspapers are typical examples of two-sided markets where the newspaper can be conceived as platforms that allow interaction between audiences ("eyeballs") and advertisers. The newspaper creates (or buys) content to attract viewers which in turn attract advertisers who pay for readers' attention.\cite{evans_industrial_2005} The size and characteristics of the audience has a positive effect on the advertisers' willingness to pay, as advertisements are typically sold based on cost per viewer, often expressed in terms of the cost of reaching a thousand viewers (CPM). Advertising can also have an effect on the recipients, which can be both negative and positive, depending on the quality of the advertising. Depending on the strength of the indirect network effects, private publisher maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}.\footnote{Public media such as Tagesschau.de do not depend on revenues from the advertising industry, which means that there is no two-way market structure.} Many traditional newspapers follow the subscription/advertising model, where the publisher charges both market sides: The audience pays a fee to obtain access to the content, and advertisers pay to obtain access to the viewers. Many online news agencies provide part of their editorial content for free and hide another, more exclusive part behind a paywall. However, since the Internet has considerably simplified the possibilities for obtaining information and thus reduced the marginal utility of content, such a business model can only be efficient if the content is very exclusive. As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many eyeballs as possible to their platform, and thus exploit the indirect network effects on the advertising site. In fact, most advertising-financed online magazines earn their gross margin from advertising.\cite{evans_industrial_2005} In order to maximize their profits, these companies have an interest in attracting as many readers as possible. Facebook is an important traffic supplier for news sites: Over 487.000 news articles from TOP15\footnote{Bild.de, bunte, Chip, FAZ, Focus, Handelsblatt, Heise, N-TV, Spiegel, Sport1, Stern, Süddeutsche, Tagesschau, Welt, Zeit} media were shared 123.000.000 times on Facebook (94\%), Twitter(3.5\%) and Google+(2.3\%).\cite{schiller_development_2016} In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site. Online advertising makes it possible to target ads to particular consumers in real time. Facebook instant articles facilitates this targeting, as they make the public users profile data available to the publisher. However, not all topics are equally often distributed in social media. \citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic. FOCUS Online for example is targeted for articles from politics and business, while sports news is more likely to be shared from Bild.de.

While these pre-defined resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics. Especially if the articles originate from different news portals. Furthermore, articles can contain more than one topic. We use a structural topic model to reveal the underlying topics of a collection of articles, and how the articles exhibit them. We then estimate the effect of topic prevalence on the number of Facebook shares. We use a data set of online news articles about domestic politics dated from 01.06.2017 to 22.11.2017\footnote{German federal elections took place on 24th of September 2017.} from seven German content providers: Bild.de, Die Welt, Focus Online, Spiegel Online, Stern.de, Zeit Online and Tagesschau.de. They are all providers of online news, whereby Tagesschau.de is the only publicly funded service. The latter was also included in the study to verify whether the topics differ when the content is created on the basis of a different business model.

@@

The two-sided market structure of news markets results in news platforms striving to choose their content in such a way that its reach is as large as possible in order to maximize profits from advertising revenues. This may lead to media-bias, as advertising may affect the ability and incentives of media to provide independent news. On the other hand, advertising may also have a positive impact on the media, as it enables publishers to report independently of political parties. \citet{ellman_what_2009} found that advertising increases the intensity of competition for readers and therefore raises accuracy of media coverage.

>>>>

In Germany, the debate about the role of public media and their mission in a rapidly changing media world is a recurring theme. If the right to use digital media were to be withdrawn from the public media outlets, they would not only be deprived of the possibility of improved information provision. They also threatened to lose their competitiveness with commercial media. But it is precisely this competitiveness that is constitutionally guaranteed. On the other hand, there is the concern of commercial providers who are registering an ever-increasing number of digital services financed by fees. They complain about a bias in competition caused by public media offering online text-content because of their fee financing. The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues.

The fundamental question in this debate is whether the offer of public news on the internet is justified. They should only occur where there are clear deficits in private sector supply. A frequently cited argument is that only the public media make it possible to provide information that is free of self-interest. Due to their public mandate and financing, they can afford what private providers cannot or only to a limited extent because of their economic dependency: a journalistic and editorial self-observation of society in the public interest. Due to their constitutional determination, they are obliged to the diversity and representation of the political and social spectrum of opinion in its entire breadth, including minority positions.

In order to check whether there is a difference in content between public and private providers, we investigate online

We use a data set of German online news articles about domestic politics to examine the differences in news content between public and private news provides. Your dataset contains articles dated from 01.06.2017 to 22.11.2017\footnote{German federal elections took place on 24th of September 2017.} from seven German content providers to analyze news reports about german elections, where we allow prevalence of topics to evolve over time (before and after the elections) and vary across newswire services. We then estimate the effect of news wire source on both topical prevalence (topic distribution) and topical content (word-topic distribution).

Mapping raw text to one or more topics, without having prior knowledge on what those topics are, translates to an unsupervised classification problem on natural language. Topic models generate low-dimensional representations of data and can uncover interesting latent structure in large text datasets. They are popular tools for automatically identifying prominent themes in text. Within topic models the Latent Dirichlet Allocation (LDA) is a widely used technique, where each document (article) is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms, represented by the topic-term distribution \citep{blei_latent_2003}. \citet{roberts_model_2016} extents the base idea of LDA by developing a structural topic model (STM) that allows to incorporate external variables that effect both topical content and topical prevalence. We use this approach to analyze online news about the german federal elections, where we allow prevalence of topics to vary across newswire services. We then estimate the effect of topical prevalence (the posterior document-topic distribution) on the ownership (public or private).

Chapter \ref{ch_model} explains the generative process of the mixed membership model and the results of this process are presented in chapter \ref{ch_results}. Chapter \ref{ch_data} contains a description of the text data and how it was pre-processed in order to use it as input variable. Chapter \ref{ch_regression} describes how we regress the estimated probabilities of topic prevalence of a document on its methadata.

@@

Advertising-supported media such as online newspapers are typical examples of two-sided markets where the newspaper can be conceived as platforms that allow interaction between audiences ("eyeballs") and advertisers. The newspaper creates (or buys) content to attract viewers which in turn attract advertisers who pay for readers' attention.\cite{evans_industrial_2005} The size and characteristics of the audience has a positive effect on the advertisers' willingness to pay, as advertisements are typically sold based on cost per viewer, often expressed in terms of the cost of reaching a thousand viewers (CPM). Advertising can also have an effect on the recipients, which can be both negative and positive, depending on the quality of the advertising. Depending on the strength of the indirect network effects, private publisher maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}. Many traditional newspapers follow the subscription/advertising model, where the publisher charges both market sides: The audience pays a fee to obtain access to the content, and advertisers pay to obtain access to the viewers. Many online news agencies provide part of their editorial content for free and hide another, more exclusive part behind a paywall. However, since the Internet has considerably simplified the possibilities for obtaining information and thus reduced the marginal utility of content, such a business model can only be efficient if the content is very exclusive. As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many eyeballs as possible to their platform, and thus exploit the indirect network effects on the advertising site. In fact, most advertising-financed online magazines earn their gross margin from advertising.\cite{evans_industrial_2005} In order to maximize their profits, these companies have an interest in attracting as many readers as possible. In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site. Online advertising makes it possible to target ads to particular consumers in real time.

The two-sided market structure of the private news markets results in news platforms striving to choose their content in such a way that its reach is as large as possible in order to maximize profits from advertising revenues. \citep{steiner_program_1952} concluded, that profit-maximizing media owners may choose to offer the same content, i.e. content aligned with the tastes of the majority. \citep{gabszewicz_press_2001} study the problem of diversity of the political content of newspapers. They find that the maximum differentiation only prevails if the readers sufficiently value the political differentiation between the newspapers the advertising market is small enough. On the other hand, advertising may also have a positive impact on the media, as it enables publishers to report independently of political parties. \citet{ellman_what_2009} found that advertising increases the intensity of competition for readers and therefore raises accuracy of media coverage.

Given the crucial role of the media in shaping opinion and promoting democracy, pluralism of opinion and accuracy of information is a major concern of public authorities. The public media in Germany was established in the post-war period and is still subject to three major main orders: (1)  In Germany, public media has the constitutional mandate to contribute to the formation of individual and public opinion, thus contributing to a well-functioning democratic society. In contrast to private media, public media do not operate on two-sided markets, but are paid out of public funds. This is intended to ensure their independence from advertiser revenue.

@@

### 2018-01-09 paper/doc/doc_public_private.tex
step

The debate about the role of public media and their mission in a rapidly changing media world is a recurring theme. If the right to use digital media were to be withdrawn from the public media outlets, they would not only be deprived of the possibility of improved information provision. They also threatened to lose their competitiveness with commercial media. But it is precisely this competitiveness that is constitutionally guaranteed. On the other hand, there is the concern of commercial providers who are registering an ever-increasing number of digital services financed by fees. They complain about a bias in competition caused by public media offering online text-content because of their fee financing. The regulator recognizes this inequality and has banned advertising and sponsorship in its online services.

The fundamental question in this debate is whether the offer of public news on the internet is justified. They should only occur where there are clear deficits in private sector supply. A frequently cited argument is that only the public media make it possible to provide information that is free of self-interest. Due to their public mandate and financing, they can afford what private providers cannot or only to a limited extent because of their economic dependency: a journalistic and editorial self-observation of society in the public interest. Due to their constitutional determination, they are obliged to the diversity and representation of the political and social spectrum of opinion in its entire breadth, including minority positions.

Markt für Online-Texte.
Presseverlage beklagen immer mehr eine Wettbewerbsverzerrung durch öffentlich-rechtliche Online-Angebote. "Wir erleben im Netz nach wie vor eine mit öffentlich-rechtlichen Geldern finanzierte Flut textbasierter Gratis-Angebote, nichts anderes als eine gebührenfinanzierte digitale Staatspresse, die den Wettbewerb verzerrt und uns Presseverlagen kaum Entfaltungsmöglichkeiten lässt" %(http://www.sz-online.de/nachrichten/ard-und-zdf-gebuehrenfinanzierte-staatspresse-3776123.html)

@@

>>>>

Social networks such as Facebook are becoming more and more important for online news services: an increasing number of their readers access the news pages via links in the networks. Users of Facebook, for example, can use their profile to share links to external websites - such as news portals - with their online friends. This has led to the development of social media becoming an important generator of traffic for content providers. In Germany, 94\% of online shared news articles in 2015 are distributed via Facebook, followed by Twitter with 3.5\% and Google+ with 2.3\% \citep{schiller_development_2016}.

The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues. For this reason, news agencies are particularly interested in finding out which topics are more likely shared on these platforms. \citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic. FOCUS Online for example is targeted for articles from politics and business, while sports news is more likely to be shared from Bild.de.

While these pre-defined resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics. Especially if the articles originate from different news portals. Furthermore, articles can contain more than one topic. We use a structural topic model to reveal the underlying topics of a collection of articles, and how the articles exhibit them. We then estimate the effect of topic prevalence on the number of Facebook shares. We use a data set of online news articles about domestic politics dated from 01.06.2017 to 22.11.2017\footnote{German federal elections took place on 24th of September 2017.} from seven German content providers: Bild.de, Die Welt, Focus Online, Spiegel Online, Stern.de, Zeit Online and Tagesschau.de. They are all providers of online news, whereby Tagesschau.de is the only publicly funded service. The latter was also included in the study to verify whether the topics differ when the content is created on the basis of a different business model.

@@

Facebook is an important traffic supplier for news sites: Over 487.000 news articles from TOP15\footnote{Bild.de, bunte, Chip, FAZ, Focus, Handelsblatt, Heise, N-TV, Spiegel, Sport1, Stern, Süddeutsche, Tagesschau, Welt, Zeit} media were shared 123.000.000 times on Facebook (94\%), Twitter(3.5\%) and Google+(2.3\%).\cite{schiller_development_2016} In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site. Online advertising makes it possible to target ads to particular consumers in real time. Facebook instant articles facilitates this targeting, as they make the public users profile data available to the publisher. However, not all topics are equally often distributed in social media.
